---
title: "Ejemplo Dashboard 2"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: cosmo
    source: embed
---

```{r setup, include=FALSE}
library(flexdashboard)
```


Página 1 {data-orientation=rows data-icon="fa-paw"}
=====================================

### Panel 1

### Panel 2

Página 2 {data-icon="fa-dove" data-orientation=rows}
=====================================

Row
-------------------------------------

### 

```{r}
valueBox(
  value = 40.5,
  caption = "Ejemplo 1",
  icon = "fa-paw",
  color = "primary"
)
```

### 

```{r}
valor_calculado <- 85

valueBox(
  value = valor_calculado,
  caption = "Ejemplo 2",
  icon = ifelse(test = valor_calculado > 50, yes = "fa-thumbs-up",
                no = "fa-thumbs-down"),
  color = ifelse(test = valor_calculado > 50, yes = "success",
                 no = "danger")
)
```

### 

```{r}
valueBox(
  value = 100,
  caption = "Ejemplo 3",
  icon = "fa-thumbs-down",
  color = "#414181"
)
```

###

```{r}
gauge(
  value = 40,
  symbol = "%",
  min = 1,
  max = 100,
  sectors = gaugeSectors(
    success = c(70, 100),
    warning = c(30, 69),
    danger = c(1, 29)
  ),
  label = "Indicador 1"
)
```


Row
-------------------------------------

### Tabla

### Gráfico

Ejemplo 1 {data-navmenu="Menú" .storyboard}
=====================================

### Ejemplo storyboard

```{r}
plot(iris)
```

### Otro ejemplo

```{r}
plot(mtcars)
```

### Este es un ejemplo de storyboard con flexdashboard en el semillero de R

```{r}
plot(Titanic)
```

***

Estas son algunas notas para este resultado:

- Viñeta 1

- Viñeta 2

- Viñeta 3

### Ejemplo A

### Ejemplo B

### Ejemplo C

Ejemplo 2 {data-navmenu="Menú"}
=====================================

Ejemplo 3 {data-navmenu="Menú"}
=====================================